---
title: "Estimates for Bahia, Brazil"
description: |
  Identifying changes in the reproduction number, rate of spread, and doubling time during the course of the COVID-19 outbreak whilst accounting for potential biases due to delays in case reporting both nationally and subnationally in Brazil These results are impacted by changes in testing effort, increases and decreases in testing effort will increase and decrease reproduction number estimates respectively (see Methods or our [paper](https://wellcomeopenresearch.org/articles/5-112/) for further explanation).
bibliography: library.bib
output:
  distill::distill_article:
    self_contained: true
categories:
  - "Subnational estimates"
  - "Americas"
---




```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.height = 12,
                      fig.width = 12,
                      dpi = 400)
```


```{r load-packages, include = FALSE}
library(EpiNow)
library(dplyr)
library(geobr)
library(magrittr)
library(rmarkdown)
library(here)
library(stringr)
library(ggplot2)
library(sf)
```

*Using data available up to the:* `r Sys.Date()`

*Note that it takes time for infection to cause symptoms, to get tested for SARS-CoV-2 infection, for a positive test to return and ultimately to enter the case data presented here. In other words, today’s case data are only informative of new infections about two weeks ago. This is reflected in the plots below, which are by date of infection.*

## Expected daily confirmed cases by city

```{r}
summary_table <- readRDS("../../../_nowcasts/covid-regional/brazil/cities-ba-summary/summary_table.rds")
region_codes <- readRDS("../../../_nowcasts/covid-regional/brazil/data/region_codes.rds")
latest_date <- readRDS("../../../_nowcasts/covid-regional/brazil/cities-ba-summary/latest_date.rds")
summary_table <- summary_table %>%
  dplyr::left_join(region_codes %>%
                     dplyr::mutate(region = region),
                   by = c("Region" = "region")) %>%
  mutate(name_muni = str_split(Region, "-", simplify = TRUE)[,2],
         state = str_split(Region, "-", simplify = TRUE)[,1])

state_abbr <- summary_table %>%
  filter(!is.na(state)) %>%
  ungroup() %>%
  pull(state) %>%
  head(1)
```

```{r map, fig.height = 6, layout="l-body-outset", out.width = "70%"}
regions <- read_municipality(code_muni= state_abbr, year = 2018,
                             showProgress = FALSE)
regions_with_data <- regions %>%
  dplyr::left_join(summary_table, by = "name_muni")
map <- ggplot2::ggplot(regions_with_data) +
  ggplot2::geom_sf(ggplot2::aes(fill = `Expected change in daily cases`),
                   alpha = 0.8, size = 0.2, col = "white")
EpiNow::theme_map(
  map,
  continuous = FALSE,
  variable_label = "Expected change in daily cases",
  fill_labels = ggplot2::waiver(),
  breaks = levels(summary_table$`Expected change in daily cases`)
  )
```

<br>
`r paste0("*Figure 1: The results of the latest reproduction number estimates (based on estimated cases with a date of infection on the ", latest_date , ") in Brazil, stratified by region, can be summarised by whether cases are likely increasing or decreasing. This represents the strength of the evidence that the reproduction number in each region is greater than or less than 1, respectively (see the [methods](https://epiforecasts.io/covid/methods.html) for details). Regions with fewer than 40 cases reported on a single day are not included in the analysis (light grey).*")`


## State summary

```{r}
## Control parameters for region-report
summary_tables <- 0
summary_figures <- 1
title_depth <- 3
index <- 1
region <- "Bahia"
region_path <- "_nowcasts/covid-regional/brazil/regional"
show_title <- FALSE
report_forecast <- TRUE
```

```{r,  child = system.file("templates/_region-report.Rmd", package = "EpiNow")}
```

### Data availability

* Case counts by date, stratified by region were downloaded from a publicly available source [@NCoVUtils; @cota_monitoring_2020].
* Case onset dates were estimated using case counts by date of report and a distribution of reporting delays fitted to a publically available line-list of cases reported internationally [@kraemer2020epidemiological; @NCoVUtils].

### Limitations

* Line-list data to inform a region specific estimate of the reporting delay were not available.
* Regions are only included if at least 40 confirmed cases have been reported on a single day.

```{r}
standalone <- FALSE
region_path <- NULL
summary_path <- "_nowcasts/covid-regional/brazil/cities-ba-summary"
```

```{r,  child = system.file("templates/_regional-summary.Rmd", package = "EpiNow")}
```
